\documentclass[]{resume-openfont}

\pagestyle{fancy}
\resetHeaderAndFooter

%--------------------------------------------------------------
% Convenience command - make it easy to fill template

% Create job position command. Parameters: company, position, location, when
\newcommand{\resumeHeading}[4]{\runsubsection{\uppercase{#1}}\descript{ | #2}\hfill\location{#3 | #4}\fakeNewLine}

% Create education heading. Parameters: Name, degree, location, when
\newcommand{\educationHeading}[3]{\runsubsection{#1}\hspace*{\fill}  \location{#3}\\
\descript{#2}\fakeNewLine}

% Create project heading. Parameters: Name, link, Tech stack
\newcommand{\projectHeading}[3]{\Project{#1}{#2}
\descript{#3}\\}

\newcommand{\projectHeadingWithDate}[4]{\Project{#1}{#2}
\descript{#3 | #4}\\}

% Parameters: courses
\newcommand{\courseWork}[1]{\textbf{Coursework:} #1}

% Parameters: courses
\newcommand{\teacherAssistant}[1]{\textbf{Teacher Assistant (TA):} #1}
 
%--------------------------------------------------------------
\begin{document}

%--------------------------------------------------------------
%     Profile
%--------------------------------------------------------------
\newcommand{\yourName}{Steven Frederiksen}
% How you want it to show up on the resume
\newcommand{\yourWebsite}{studeo14.github.io}
% vs how you want it to show up. If it's you can just replace "\yourWebsiteLink" with "yourWebsite"
\newcommand{\yourWebsiteLink}{https://studeo14.github.io}
\newcommand{\yourEmail}{vkabrich@gmail.com}
\newcommand{\yourPhone}{540-809-5804}
\newcommand{\githubUserName}{studeo14}
\newcommand{\linkedInUserName}{steven-frederiksen-215a65117}

% An alternate profile section 
% \alignProfileTable
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%     \ralewayBold{\href{\yourWebsiteLink}{\Large \yourName}} & 
%     Email : \href{mailto:\yourEmail}{\yourEmail}
%     \\
%     \href{https://github.com/\githubUserName}{GitHub://\githubUserName} & 
%     Mobile : \yourPhone
%     \\
%     \href{https://www.linkedin.com/in/\linkedInUserName}{LinkedIn://\linkedInUserName} & Website : \href{\yourWebsiteLink}{\yourWebsite}
%     \\
% \end{tabular*}

\begin{center}
    \Huge \scshape \latoRegular{\yourName} \\ \vspace{1pt}
    \small \href{mailto:\yourEmail}{\underline{\yourEmail}}  $|$  \yourPhone $|$ 
    \href{https://www.linkedin.com/in/\linkedInUserName}{\underline{linkedIn/\linkedInUserName}} $|$
    \href{https://github.com/\githubUserName}{\underline{github/\githubUserName}} 
    % $|$ \href{\yourWebsiteLink}{\underline{\yourWebsite}}
\end{center}

%--------------------------------------------------------------
%     Experience
%--------------------------------------------------------------
\section{Work Experience}
\resumeHeading{Graf Research}{Research Engineer}{Blacksburg, VA}{2018 – present}
\begin{bullets}
    \item Led development of real-time, in-FPGA test bench platform for custom IP utilizing Vivado Model Composer and Vivado HLS for creation of generic interfaces, Simulink for simulation and test vector generation, and an Ethernet-based protocol for data transfer between test harness and user machine.
    \item Modeling, simulation, and implementation of DSP algorithms in FPGAs.
    \item Led development of Lattice-specific functionality for Graf Trace tool, which archives and verifies build artifacts throughout an FPGA build flow, enabling customers to meet new DoD guidance.
    \item Transitioned M.S. research to product prototype with Graf DELV software. DELV translates English specifications to System Verilog assertions for automatic verification of HDL.
    \item Led transition to Vue.js and deployment using Docker/Kubernetes for internal web-application product. Also performed full-stack development for the same project using Spring/Vue.
    \item Experience utilizing Python for internal tooling including: automated FPGA design instrumentation and testing, custom lab bench software, GUI and CLI application prototypes.
    \item Wrote and contributed to multiple winning Phase 1 and 2 SBIR proposals
    \item Kept up to date with state-of-the-art hardware trojan literature in service of SBIR contracts.
\end{bullets}
\textbf{Publications}: "DELV: Datasheet/English to Logic Verification," Edward Carlisle, Steven Frederikson, Jonathan Graf, Scott Harper, John Aromando, and Michael S. Hsiao, in \textit{Government Microcircuit Applications \& Critical Technology Conf}., Mar. 2021.
\sectionsep

%--------------------------------------------------------------
%     Projects
%--------------------------------------------------------------
\section{Projects}

\projectHeading{ESP32 Environmental controller}{https://github.com/studeo14/Environment-Controller}{ESP32, FreeRTOS, IoT}
Custom environemtal control and monitoring solution for fermentation projects.
\begin{bullets}
    \item Live monitoring and control via MQTT
    \item I2C control and monitoring chain for sensors and relays.
    \item Uses ESP-IDF for FreeRTOS integration.
\end{bullets}
\sectionsep

\projectHeading{Ray Tracing Animations}{https://github.com/studeo14/Ray-Tracing}{Rust, Computer Graphics, Data Transformation}
Implemented a simple ray-tracer in Rust.
\begin{bullets}
    \item Implement a ray tracer to render a scene with multiple material types.
    \item Improve upon the original object model with Rust traits and module organization.
    \item Multi-threading using the threadpool crate on a per-pixel basis.
    \item Linear animation of any object in the scene (including camera) using an Iterator-based design to facilitate composition of mutliple animations and automatic history of object states.
\end{bullets}
\sectionsep

\projectHeading{TTSA}{https://bitbucket.org/studeo14/simulated-annealing-ttsa}{Rust, EDA Algorithms, Optimzation, Simulated Annealing}
Implementation of the \href{https://www.researchgate.net/publication/220813632_A_Simulated_Annealing_Approach_to_the_Travelling_Tournament_Problem}{TTSA} algorithm using Rust.
\sectionsep

% Example using bullets and dates 
% \projectHeadingWithDate{Hogwart\textquotesingle{}s Library Management System}{https://github.com/Aarif123456/hogwartslibrary}{PHP, JavaScript, HTML, CSS, MySQL}{Aug 2019}
% \begin{bullets}
    % \item A full-stack library management system, where users can manage books and holds on their accounts. Users can search the library\textquotesingle{}s catalogue, which has every book mentioned in the Harry Potter series. The system distinguishes between 4 users. For examples, librarians who can also check or return books on behalf of users.\\
% \end{bullets}
% \sectionsep
  

%--------------------------------------------------------------
%     Skills
%--------------------------------------------------------------
\section{Skills}

% A more concise alternate 
\begin{skillList}
    \singleItem{Languages:}{Java, C/C++, Python, Rust, Bash, Javascript, Lisp, MATLAB}%
    \\
    \singleItem{FPGA Development:}{Verilog, Vivado HLS, Verilator, Symbiflow, ABV, Simulink/Model Composer, SystemVerilog/SVA}
    \\
    \singleItem{Technology:}{Microblaze, ESP-IDF, FreeRTOS, Arduino, HTML/CSS, Git, Docker, Kubernetes, XMIDAS, \LaTeX}%
    \\
    \singleItem{Communication:}{SBIR proposals, technical progress and final reports, journal article (\href{https://doi.org/10.1109/ITC44778.2020.9325264}{link}), Patent applications}
\end{skillList}
\sectionsep

%--------------------------------------------------------------
%     Education
%--------------------------------------------------------------
\section{Education}
% Put school first and degree second if your school is reputable
\educationHeading{B.S. Computer Engineering}{Virginia Tech}{Blacksburg, VA}
\end{document}
